``Interestingness'' in Mathematical Theory Exploration

### 2019-11-29 PhDThesis/background_machinelearning.tex
Fix recursive ML equations

Particularly relevant to our work is the ability for distributed representations
to approximate recursive data such as syntax trees. This is achieved by defining
(or learning) functions to \emph{combine} the representations of parts into
those of composite objects, to \emph{test} whether or not a given feature vector
represents a composite object, and to \emph{project} composite representations
back into those of their constituents. For example, if $c$ and $d$ are the
compression and decompression routines of an auto-encoder for non-recursive
data, we can define an auto-encoder ($c'$ and $d'$) for binary trees in terms
of a combining function $\bigoplus$, a predicate $\texttt{node?}$ and projection
functions $\pi_{left}}$ and $\pi_{right}}$ as follows:

\begin{equation*}
  c'(x) = \begin{cases}
            c'(a) \bigoplus c'(b) & \text{if $x = \texttt{node}(a, b)$}
            c(x)                  & \text{otherwise}
          \end{cases}

  d'(x) = \begin{cases}
            \texttt{node}(d'(\pi_{left }(x)),
                          d'(\pi_{right}(x))) & \text{if \texttt(node?)(x)}
            d(x)                            & \text{otherwise}
          \end{cases}
\end{equation*}

>>>>

Particularly relevant to our work is the ability for distributed representations
to approximate recursive data such as syntax trees. This is achieved by defining
(or learning) functions to \emph{combine} the representations of parts into
those of composite objects, to \emph{test} whether or not a given feature vector
represents a composite object, and to \emph{project} composite representations
back into those of their constituents. For example, if $c$ and $d$ are the
compression and decompression routines of an auto-encoder for non-recursive
data, we can define an auto-encoder ($c'$ and $d'$) for binary trees in terms
of a combining function $\bigoplus$, a predicate $\texttt{node?}$ and projection
functions $\pi_{left}$ and $\pi_{right}$ as follows:

\begin{align*}
  c'(x) &= \begin{cases}
             c'(a) \bigoplus c'(b) & \text{if $x = \texttt{node}(a, b)$} \\
             c(x)                  & \text{otherwise}
           \end{cases} \\
  d'(x) &= \begin{cases}
             \texttt{node}(d'(\pi_{left }(x)),
                           d'(\pi_{right}(x))) & \text{if \texttt{node?}(x)} \\
             d(x)                              & \text{otherwise}
           \end{cases}
\end{align*}
